KidsAIR: Main analysis initial steps

### 2021-06-09 main_analysis_initial.Rmd
PM analysis updates. Manuscript revisions from co-author comments.

# Merge dataset with blinded treatments and final LRTI data, select analysis variables
kids_analysis_data_1obs_per_child <- health_exposure_data_sampling_day %>% 
  #select(-treatment_assigned, -treatment_actual) %>% 
  mutate(child_age = fct_collapse(age_child_nov,
                                  "< 1" = "Less than 1",
                                  "1+" = c(1, 2, 3, 4))) %>% 
  left_join(treatments_masked, by = "home") %>% 
  arrange(area, home, child_id_num, winter_id, age_child_nov) %>% 
  right_join(lrti_1obs_total, by = c("area", "home", "child_id_num")) %>% 
  left_join(kids_filter_compliance_total, by = c("area", "home")) %>% 
  distinct(area, child_id_num, .keep_all = TRUE) %>% 
  dplyr::select(area, home, cohort, child_id_num, child_age, lrti_events_total, 
         person_time_at_risk_total, lrti_incidence_total, newtx, treatment_assigned,
         amb_pm_lrti, amb_temp_lrti, amb_dewp_lrti, amb_pressure_lrti, amb_wind_lrti, gender,
         gender_parent, hispanic_parent, race_parent, education_3level, income_3level,
         home_floors_2level, home_year_built_2level, home_pets_2level, home_pets,
         stove_age_3level, chimney_clean_3level, wood_collect_method_2level, home_sqft_2level,
         wood_collect_2level, stove_grade_3level, burn_level_3level, ruca_code,
         ruca_code_2, ruca_code_3, residents_smoke, residents_smoke_inside,
         residents_under_five, home_bedrooms, pm_mean_sampling_period, 
         pm_sample_interval, pm_at_home_sampling_period,
         moisture_closest, temp_indoor_max, rh_indoor_max, sums_events_sampling_period_2.5,
         sums_events_sampling_period_5, sums_events_sampling_period_7.5,
         home_act_smoking_sum, home_act_windows_sum, home_act_sweep_sum, home_act_door_sum,
         filter_type, filter_compliance) %>% 
  rename(treatment = newtx,
         person_time_at_risk = person_time_at_risk_total) %>% 
  mutate(log_person_time_at_risk = log(person_time_at_risk)) %>% 
  mutate(lrti_events_di_total = if_else(lrti_events_total == 0, 0, 1),
         treatment_filter_type = as.character(treatment_assigned),
         filter_type = as.character(filter_type),
         treatment_filter_type = if_else(treatment_filter_type == "Filter", 
                                         filter_type, treatment_filter_type),
         treatment_filter_type = factor(treatment_filter_type,
                                        levels = c("Placebo", "Education", 
                                                   "Honeywell", "Large Filtrete", 
                                                   "Small Filtrete", "Winix")),
         filter_compliance2 = as.character(filter_compliance),
         filter_compliance2 = if_else(treatment_assigned == "Education", treatment_assigned, filter_compliance2),
         filter_compliance = factor(filter_compliance2,
                                  levels = c("Placebo", "Education", 
                                             "0-25 compliance", "25-50 compliance",
                                             "50-75 compliance", "75-100 compliance"))) %>% 
  mutate(treatment = factor(treatment,
                            levels = c("Blackfoot", "Dearborn", "Smith")),
         treatment_assigned = factor(treatment_assigned,
                                     levels = c("Placebo", "Filter", "Education")))

@@

kids_analysis_data_2obs_per_child <- health_exposure_data_sampling_day %>% 
  #select(-treatment_assigned, -treatment_actual) %>% 
  mutate(child_age = fct_collapse(age_child_nov,
                                  "< 1" = "Less than 1",
                                  "1+" = c(1, 2, 3, 4))) %>% 
  left_join(treatments_masked, by = "home") %>% 
  arrange(area, home, child_id_num, winter_id, age_child_nov) %>% 
  right_join(lrti_1obs_per_winter, by = c("area", "home", "child_id_num", "winter_id")) %>%  
  left_join(kids_filter_compliance_winter1, by = c("area", "home_winter_id")) %>% 
  distinct(area, child_id_num, winter_id, .keep_all = TRUE) %>% 
  dplyr::select(area, home, cohort, child_id_num, home_winter_id, winter_id, child_age, 
         amb_pm_lrti, amb_temp_lrti, amb_dewp_lrti, amb_pressure_lrti, amb_wind_lrti, gender,
         lrti_events_winter, person_time_at_risk_winter, lrti_incidence_winter, newtx, treatment_assigned,
         gender_parent, hispanic_parent, race_parent, education_3level, income_3level,
         home_floors_2level, home_year_built_2level, home_pets_2level, home_pets,
         stove_age_3level, chimney_clean_3level, wood_collect_method_2level, home_sqft_2level,
         wood_collect_2level, stove_grade_3level, burn_level_3level, ruca_code,
         ruca_code_2, ruca_code_3, residents_smoke, residents_smoke_inside,
         residents_under_five, home_bedrooms, pm_mean_sampling_period, 
         pm_sample_interval, pm_at_home_sampling_period,
         moisture_closest, temp_indoor_max, rh_indoor_max, sums_events_sampling_period_2.5,
         sums_events_sampling_period_5, sums_events_sampling_period_7.5,
         home_act_smoking_sum, home_act_windows_sum, home_act_sweep_sum, home_act_door_sum,
         filter_type, filter_compliance) %>% 
  rename(treatment = newtx) %>% 
  mutate(log_person_time_at_risk_winter = log(person_time_at_risk_winter)) %>% 
  mutate(lrti_events_di_winter = if_else(lrti_events_winter == 0, 0, 1),
         treatment_filter_type = as.character(treatment_assigned),
         filter_type = as.character(filter_type),
         treatment_filter_type = if_else(treatment_filter_type == "Filter", 
                                         filter_type, treatment_filter_type),
         treatment_filter_type = factor(treatment_filter_type,
                                        levels = c("Placebo", "Education", 
                                                   "Honeywell", "Large Filtrete", 
                                                   "Small Filtrete", "Winix")),
         filter_compliance2 = as.character(filter_compliance),
         filter_compliance2 = if_else(treatment_assigned == "Education", treatment_assigned, filter_compliance2),
         filter_compliance = factor(filter_compliance2,
                                  levels = c("Placebo", "Education", 
                                             "0-25 compliance", "25-50 compliance",
                                             "50-75 compliance", "75-100 compliance"))) %>% 
  mutate(treatment = factor(treatment,
                            levels = c("Blackfoot", "Dearborn", "Smith")),
         treatment_assigned = factor(treatment_assigned,
                                     levels = c("Placebo", "Filter", "Education")))

@@

```{r}
# Summary analysis for categorical variables

# clean up data for table 1 summary
table_1_data <- health_exposure_data_sampling_day %>% 
  mutate(treatment_assigned = factor(treatment_assigned,
                                     levels = c("Placebo", "Filter", "Education"))) %>% 
    #select(-treatment_assigned, -treatment_actual) %>% 
  #left_join(treatments_masked, by = "home") %>%
  #rename(treatment = newtx) %>% 
  arrange(area, home, winter_id, sampling_day) %>% 
  filter(winter_id == 1) %>% 
  filter(area == "AK") %>% # Change area filter as necessary
  distinct(area, home, .keep_all = TRUE)

# summary data for manuscript tables
char_funct_total <- function(var, data = table_1_data){

demographics_summary <- data %>% 
  rename(new_var = var) %>% 
  mutate(total_n = n()) %>% 
  group_by(new_var) %>% 
  mutate(n = n(),
         percent = round(n()/total_n*100)) %>% 
  distinct(new_var, .keep_all = TRUE) %>% 
  dplyr::select(new_var, n, percent) %>% 
  arrange(new_var)
demographics_summary
}

char_funct_treatment <- function(var, data = table_1_data){

demographics_summary <- data %>% 
  rename(new_var = var) %>% 
  group_by(treatment_assigned) %>% 
  mutate(treatment_n = n()) %>% 
  group_by(treatment_assigned, new_var) %>% 
    mutate(n = n(),
         percent = round(n()/treatment_n*100)) %>% 
  distinct(new_var, .keep_all = TRUE) %>% 
  dplyr::select(new_var, n, percent) %>% 
  arrange(treatment_assigned, new_var)
demographics_summary
}

char_funct_total("gender_parent")
char_funct_treatment("gender_parent")
char_funct_total("race_parent")
char_funct_treatment("race_parent")
char_funct_total("education_3level")
char_funct_treatment("education_3level")
char_funct_total("income_3level")
char_funct_treatment("income_3level")
char_funct_total("home_floors_2level")
char_funct_treatment("home_floors_2level")
char_funct_total("home_year_built_2level")
char_funct_treatment("home_year_built_2level")
char_funct_total("home_pets_2level")
char_funct_treatment("home_pets_2level")
char_funct_total("home_pets_3level")
char_funct_treatment("home_pets_3level")
char_funct_total("residents_smoke")
char_funct_treatment("residents_smoke")
char_funct_total("residents_smoke_inside")
char_funct_treatment("residents_smoke_inside")
char_funct_total("stove_age_3level")
char_funct_treatment("stove_age_3level")
char_funct_total("chimney_clean_3level")
char_funct_treatment("chimney_clean_3level")
char_funct_total("wood_collect_method_2level")
char_funct_treatment("wood_collect_method_2level")
char_funct_total("wood_collect_2level")
char_funct_treatment("wood_collect_2level")
char_funct_total("stove_grade_3level")
char_funct_treatment("stove_grade_3level")
char_funct_total("burn_level_3level")
char_funct_treatment("burn_level_3level")
char_funct_total("ruca_code")
char_funct_treatment("ruca_code")
char_funct_total("ruca_code_2")
char_funct_treatment("ruca_code_2")
char_funct_total("ruca_code_3")
char_funct_treatment("ruca_code_3")
char_funct_total("home_act_smoking_sum")
char_funct_treatment("home_act_smoking_sum")
char_funct_total("home_act_windows_sum")
char_funct_treatment("home_act_windows_sum")
char_funct_total("home_act_sweep_sum")
char_funct_treatment("home_act_sweep_sum")
char_funct_total("home_act_door_sum")
char_funct_treatment("home_act_door_sum")
```

@@

# clean up data for table 1 summary
table_1_data <- health_exposure_data_sampling_day %>% 
  mutate(treatment_assigned = factor(treatment_assigned,
                                     levels = c("Placebo", "Filter", "Education"))) %>% 
  #select(-treatment_assigned, -treatment_actual) %>% 
  #left_join(treatments_masked, by = "home") %>%
  #rename(treatment = newtx) %>% 
  arrange(area, home, winter_id, sampling_day) %>% 
  filter(winter_id == 1) %>% 
  #filter(area == "AK") %>% # Change area filter as necessary
  distinct(area, home, .keep_all = TRUE)

# summary data for manuscript tables
num_funct_total <- function(var, data = table_1_data){

demographics_summary <- data %>% 
  rename(new_var = var) %>% 
  mutate(new_var = as.numeric(new_var)) %>% 
  #mutate(new_var = (as.numeric(new_var)-32)*5/9) %>% 
  filter(!is.na(new_var)) %>% 
  select(treatment_assigned, home, new_var) %>% 
  summarize(mean_var = mean(new_var), sd_var = sd(new_var), n_var = n(), 
            min_var = min(new_var), med_var = median(new_var), max_var = max(new_var))
demographics_summary
}

num_funct_treatment <- function(var, data = table_1_data){

demographics_summary <- data %>% 
  rename(new_var = var) %>%
  mutate(new_var = as.numeric(new_var)) %>% 
  #mutate(new_var = (as.numeric(new_var)-32)*5/9) %>%
  filter(!is.na(new_var)) %>% 
  select(treatment_assigned, home, new_var) %>% 
  group_by(treatment_assigned) %>% 
  summarize(mean_var = mean(new_var), sd_var = sd(new_var), n_var = n(), 
            min_var = min(new_var), med_var = median(new_var), max_var = max(new_var))
demographics_summary
}

@@

# Initial summary data for LRTI
incidence_summary <- analysis_data %>% 
  filter(area == "NN") %>% # Change area filter as necessary  
  #group_by(treatment) %>% # Change treatment grouping as necessary  
  #filter(lrti_incidence < 0.7) %>% 
  summarize(mean_inc = mean(lrti_incidence, na.rm = TRUE),
            sd_inc = sd(lrti_incidence, na.rm = TRUE),
            n_inc = n(),
            min_inc = min(lrti_incidence, na.rm = TRUE),
            median_inc = median(lrti_incidence, na.rm = TRUE),
            max_inc = max(lrti_incidence, na.rm = TRUE))
incidence_summary

>>>>

# Merge dataset with blinded treatments and final LRTI data, select analysis variables
kids_analysis_data_1obs_per_child <- health_exposure_data_sampling_day %>% 
  #select(-treatment_assigned, -treatment_actual) %>% 
  mutate(child_age = fct_collapse(age_child_nov,
                                  "< 1" = "Less than 1",
                                  "1+" = c(1, 2, 3, 4)),
         home_sqft_2level = cut(home_sqft, breaks = c(0, 1400, 100000),
                                labels = c("<130 sq m", "130+ sq m"))) %>% 
  left_join(treatments_masked, by = "home") %>% 
  arrange(area, home, child_id_num, winter_id, age_child_nov) %>% 
  right_join(lrti_1obs_total, by = c("area", "home", "child_id_num")) %>% 
  left_join(kids_filter_compliance_total, by = c("area", "home")) %>% 
  distinct(area, child_id_num, .keep_all = TRUE) %>% 
  dplyr::select(area, home, cohort, child_id_char, child_id_num, child_age, race_child, hispanic_child, lrti_events_total, 
         person_time_at_risk_total, lrti_incidence_total, newtx, treatment_assigned,
         amb_pm_lrti, amb_temp_lrti, amb_dewp_lrti, amb_pressure_lrti, amb_wind_lrti, gender,
         gender_parent, hispanic_parent, race_parent, education_3level, income_3level,
         home_floors_2level, home_year_built_2level, home_pets_2level, home_pets,
         stove_age_3level, chimney_clean_3level, wood_collect_method_2level, home_sqft_2level,
         wood_collect_2level, stove_grade_3level, burn_level_3level, ruca_code,
         ruca_code_2, ruca_code_3, residents_smoke, residents_smoke_inside,
         residents_under_five, home_bedrooms, pm_mean_sampling_period, 
         pm_sample_interval, pm_at_home_sampling_period,
         moisture_closest, temp_indoor_max, rh_indoor_max, sums_events_sampling_period_2.5,
         sums_events_sampling_period_5, sums_events_sampling_period_7.5,
         home_act_smoking_sum, home_act_windows_sum, home_act_sweep_sum, home_act_door_sum,
         filter_type, filter_compliance) %>% 
  rename(treatment = newtx,
         person_time_at_risk = person_time_at_risk_total) %>% 
  mutate(log_person_time_at_risk = log(person_time_at_risk)) %>% 
  mutate(lrti_events_di_total = if_else(lrti_events_total == 0, 0, 1),
         treatment_filter_type = as.character(treatment_assigned),
         filter_type = as.character(filter_type),
         treatment_filter_type = if_else(treatment_filter_type == "Filter", 
                                         filter_type, treatment_filter_type),
         treatment_filter_type = factor(treatment_filter_type,
                                        levels = c("Placebo", "Education", 
                                                   "Honeywell", "Large Filtrete", 
                                                   "Small Filtrete", "Winix")),
         filter_compliance2 = as.character(filter_compliance),
         filter_compliance2 = if_else(treatment_assigned == "Education", treatment_assigned, filter_compliance2),
         filter_compliance = factor(filter_compliance2,
                                  levels = c("Placebo", "Education", 
                                             "0-25 compliance", "25-50 compliance",
                                             "50-75 compliance", "75-100 compliance"))) %>% 
  mutate(treatment = factor(treatment,
                            levels = c("Blackfoot", "Dearborn", "Smith")),
         treatment_assigned = factor(treatment_assigned,
                                     levels = c("Placebo", "Filter", "Education")))

@@

kids_analysis_data_2obs_per_child <- health_exposure_data_sampling_day %>% 
  #select(-treatment_assigned, -treatment_actual) %>% 
  mutate(child_age = fct_collapse(age_child_nov,
                                  "< 1" = "Less than 1",
                                  "1+" = c(1, 2, 3, 4)),
         home_sqft_2level = cut(home_sqft, breaks = c(0, 1400, 100000),
                                labels = c("<130 sq m", "130+ sq m"))) %>% 
  left_join(treatments_masked, by = "home") %>% 
  arrange(area, home, child_id_num, winter_id, age_child_nov) %>% 
  right_join(lrti_1obs_per_winter, by = c("area", "home", "child_id_num", "winter_id")) %>%  
  left_join(kids_filter_compliance_winter1, by = c("area", "home_winter_id")) %>% 
  distinct(area, child_id_num, winter_id, .keep_all = TRUE) %>% 
  dplyr::select(area, home, cohort, child_id_char, child_id_num, home_winter_id, winter_id, child_age, race_child, hispanic_child,
         amb_pm_lrti, amb_temp_lrti, amb_dewp_lrti, amb_pressure_lrti, amb_wind_lrti, gender,
         lrti_events_winter, person_time_at_risk_winter, lrti_incidence_winter, newtx, treatment_assigned,
         gender_parent, hispanic_parent, race_parent, education_3level, income_3level,
         home_floors_2level, home_year_built_2level, home_pets_2level, home_pets,
         stove_age_3level, chimney_clean_3level, wood_collect_method_2level, home_sqft_2level,
         wood_collect_2level, stove_grade_3level, burn_level_3level, ruca_code,
         ruca_code_2, ruca_code_3, residents_smoke, residents_smoke_inside,
         residents_under_five, home_bedrooms, pm_mean_sampling_period, 
         pm_sample_interval, pm_at_home_sampling_period,
         moisture_closest, temp_indoor_max, rh_indoor_max, sums_events_sampling_period_2.5,
         sums_events_sampling_period_5, sums_events_sampling_period_7.5,
         home_act_smoking_sum, home_act_windows_sum, home_act_sweep_sum, home_act_door_sum,
         filter_type, filter_compliance) %>% 
  rename(treatment = newtx) %>% 
  mutate(log_person_time_at_risk_winter = log(person_time_at_risk_winter)) %>% 
  mutate(lrti_events_di_winter = if_else(lrti_events_winter == 0, 0, 1),
         treatment_filter_type = as.character(treatment_assigned),
         filter_type = as.character(filter_type),
         treatment_filter_type = if_else(treatment_filter_type == "Filter", 
                                         filter_type, treatment_filter_type),
         treatment_filter_type = factor(treatment_filter_type,
                                        levels = c("Placebo", "Education", 
                                                   "Honeywell", "Large Filtrete", 
                                                   "Small Filtrete", "Winix")),
         filter_compliance2 = as.character(filter_compliance),
         filter_compliance2 = if_else(treatment_assigned == "Education", treatment_assigned, filter_compliance2),
         filter_compliance = factor(filter_compliance2,
                                  levels = c("Placebo", "Education", 
                                             "0-25 compliance", "25-50 compliance",
                                             "50-75 compliance", "75-100 compliance"))) %>% 
  mutate(treatment = factor(treatment,
                            levels = c("Blackfoot", "Dearborn", "Smith")),
         treatment_assigned = factor(treatment_assigned,
                                     levels = c("Placebo", "Filter", "Education")))

@@

```{r}
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")

analysis_data <- read_rds(paste0(file_path, 
                                 "Output/kids_analysis_data_1obs_per_child.rds"))

# Summary analysis for categorical variables

# summary data for manuscript tables
char_funct_total <- function(var, data = health_exposure_data_sampling_day){

demographics_summary <- data %>% 
  filter(winter_id == 1) %>% 
  rename(new_var = var) %>% 
  arrange(area, home, new_var) %>% 
  distinct(area, home, .keep_all = T) %>% 
  mutate(total_n = n()) %>% 
  group_by(new_var) %>% 
  mutate(n = n(),
         percent = round(n()/total_n*100)) %>% 
  distinct(new_var, .keep_all = TRUE) %>% 
  dplyr::select(new_var, n, percent) %>% 
  arrange(new_var)
demographics_summary
}

char_funct_treatment <- function(var, data = health_exposure_data_sampling_day){

demographics_summary <- data %>% 
  filter(winter_id == 1) %>% 
  rename(new_var = var) %>% 
  arrange(area, home, new_var) %>% 
  distinct(area, home, .keep_all = T) %>% 
  group_by(treatment_assigned) %>% 
  mutate(treatment_n = n()) %>% 
  group_by(treatment_assigned, new_var) %>% 
    mutate(n = n(),
         percent = round(n()/treatment_n*100)) %>% 
  distinct(new_var, .keep_all = TRUE) %>% 
  dplyr::select(new_var, n, percent) %>% 
  arrange(treatment_assigned, new_var)
demographics_summary
}

char_funct_total("gender_parent")
char_funct_treatment("gender_parent")
char_funct_total("race_parent")
char_funct_treatment("race_parent")
char_funct_total("education_3level")
char_funct_treatment("education_3level")
char_funct_total("income_3level")
char_funct_treatment("income_3level")
char_funct_total("home_floors_2level")
char_funct_treatment("home_floors_2level")
char_funct_total("home_year_built_2level")
char_funct_treatment("home_year_built_2level")
char_funct_total("home_pets_2level")
char_funct_treatment("home_pets_2level")
char_funct_total("home_pets_3level")
char_funct_treatment("home_pets_3level")
char_funct_total("residents_smoke")
char_funct_treatment("residents_smoke")
char_funct_total("residents_smoke_inside")
char_funct_treatment("residents_smoke_inside")
char_funct_total("stove_age_3level")
char_funct_treatment("stove_age_3level")
char_funct_total("chimney_clean_3level")
char_funct_treatment("chimney_clean_3level")
char_funct_total("wood_collect_method_2level")
char_funct_treatment("wood_collect_method_2level")
char_funct_total("wood_collect_2level")
char_funct_treatment("wood_collect_2level")
char_funct_total("stove_grade_3level")
char_funct_treatment("stove_grade_3level")
char_funct_total("burn_level_3level")
char_funct_treatment("burn_level_3level")
char_funct_total("ruca_code")
char_funct_treatment("ruca_code")
char_funct_total("ruca_code_2")
char_funct_treatment("ruca_code_2")
char_funct_total("ruca_code_3")
char_funct_treatment("ruca_code_3")
char_funct_total("home_act_smoking_sum")
char_funct_treatment("home_act_smoking_sum")
char_funct_total("home_act_windows_sum")
char_funct_treatment("home_act_windows_sum")
char_funct_total("home_act_sweep_sum")
char_funct_treatment("home_act_sweep_sum")
char_funct_total("home_act_door_sum")
char_funct_treatment("home_act_door_sum")

# Summary analysis for categorical variables - by distinct child

# summary data for manuscript tables
char_funct_total <- function(var, data = health_exposure_data_sampling_day){

demographics_summary <- data %>% 
  mutate(child_age = fct_collapse(age_child_nov,
                                  "< 1" = "Less than 1",
                                  "1+" = c(1, 2, 3, 4))) %>% 
  filter(winter_id == 1) %>% 
  filter(!is.na(child_id_char)) %>% 
  rename(new_var = var) %>% 
  arrange(area, child_id_char, new_var) %>% 
  distinct(area, child_id_char, .keep_all = T) %>% 
  mutate(total_n = n()) %>% 
  group_by(new_var) %>% 
  mutate(n = n(),
         percent = round(n()/total_n*100)) %>% 
  distinct(new_var, .keep_all = TRUE) %>% 
  dplyr::select(new_var, n, percent) %>% 
  arrange(new_var)
demographics_summary
}

char_funct_treatment <- function(var, data = health_exposure_data_sampling_day){

demographics_summary <- data %>% 
  mutate(child_age = fct_collapse(age_child_nov,
                                  "< 1" = "Less than 1",
                                  "1+" = c(1, 2, 3, 4))) %>% 
  filter(winter_id == 1) %>% 
  rename(new_var = var) %>% 
  arrange(area, child_id_char, new_var) %>% 
  distinct(area, child_id_char, .keep_all = T) %>% 
  group_by(treatment_assigned) %>% 
  mutate(treatment_n = n()) %>% 
  group_by(treatment_assigned, new_var) %>% 
    mutate(n = n(),
         percent = round(n()/treatment_n*100)) %>% 
  distinct(new_var, .keep_all = TRUE) %>% 
  dplyr::select(new_var, n, percent) %>% 
  arrange(treatment_assigned, new_var)
demographics_summary
}

char_funct_total("gender")
char_funct_treatment("gender")
char_funct_total("child_age")
char_funct_treatment("child_age")
char_funct_total("race_child")
char_funct_treatment("race_child")
char_funct_total("hispanic_child")
char_funct_treatment("hispanic_child")
```

@@

# summary data for manuscript tables
num_funct_total <- function(var, data = health_exposure_data_sampling_day){

demographics_summary <- data %>% 
  filter(winter_id == 1) %>% 
  rename(new_var = var) %>% 
  arrange(area, home, new_var) %>% 
  distinct(area, home, .keep_all = T) %>% 
  mutate(new_var = as.numeric(new_var)) %>% 
  #mutate(new_var = (as.numeric(new_var)-32)*5/9) %>% 
  filter(!is.na(new_var)) %>% 
  dplyr::select(treatment_assigned, home, new_var) %>% 
  summarize(mean_var = mean(new_var), sd_var = sd(new_var), n_var = n(), 
            min_var = min(new_var), med_var = median(new_var), max_var = max(new_var))
demographics_summary
}

num_funct_treatment <- function(var, data = health_exposure_data_sampling_day){

demographics_summary <- data %>% 
  filter(winter_id == 1) %>% 
  rename(new_var = var) %>% 
  arrange(area, home, new_var) %>% 
  distinct(area, home, .keep_all = T) %>% 
  mutate(new_var = as.numeric(new_var)) %>% 
  #mutate(new_var = (as.numeric(new_var)-32)*5/9) %>%
  filter(!is.na(new_var)) %>% 
  dplyr::select(treatment_assigned, home, new_var) %>% 
  group_by(treatment_assigned) %>% 
  summarize(mean_var = mean(new_var), sd_var = sd(new_var), n_var = n(), 
            min_var = min(new_var), med_var = median(new_var), max_var = max(new_var))
demographics_summary
}

@@

# Initial summary data for LRTI
incidence_summary <- analysis_data %>% 
  #filter(!is.na(child_id_char)) %>% 
  filter(area == "WMT") %>% # Change area filter as necessary  
  #group_by(treatment) %>% # Change treatment grouping as necessary  
  #filter(lrti_incidence < 0.7) %>% 
  summarize(mean_inc = mean(lrti_incidence_total, na.rm = TRUE),
            sd_inc = sd(lrti_incidence_total, na.rm = TRUE),
            n_inc = n(),
            min_inc = min(lrti_incidence_total, na.rm = TRUE),
            median_inc = median(lrti_incidence_total, na.rm = TRUE),
            max_inc = max(lrti_incidence_total, na.rm = TRUE))
incidence_summary
